---
title             : "New Lab 8 Title"
shorttitle        : "lab8"

author: 
  - name          : "Angela Lee"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "1451 Onyx Street, Eugene, OR 97403"
    email         : "alee12@uoregon.edu"
  - name          : "Ruby Cuellar"
    affiliation   : "1"
  - name          : "Ellen Huang"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "University of Oregon"


abstract: |
  Soon our _**awesome**_ abstract will go here. 
  

keywords          : "psychology, rmarkdown, data science"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library(knitr)
library(kableExtra)
library("papaja")
library(ggplot2)
library(here)
library(rio)
library(janitor)
library(dplyr)
opts_chunk$set(echo = FALSE, fig.width = 6.5, fig.height = 8)
```

```{r data import}
data<-import(here("data","star.csv")) %>% 
  clean_names()

data$frl <- as.factor(data$frl)
```


# Commit 3
Cognitive behavioral therapy (CBT) is one of the most effective psychotherapies for psychological disorders [@zettle2015]. Trauer et al. [-@trauer2015CBT] conducted a meta-analysis on the efficacy of CBT for insomnia.

# Results
```{r eval = TRUE, echo = FALSE}
data2 <- data %>%
  select(sex, frl, tmathss, treadss)

summary_sex_frl <- data2 %>%
  group_by(sex, frl) %>%
  summarize(math_mean = mean(tmathss),
            math_sd = sd(tmathss),
            rdg_mean = mean(treadss),
            rdg_sd = sd(treadss))

kable(summary_sex_frl) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```
The mean math score and standard deviation for boys under the no frl condition was `r as.numeric(summary_sex_frl[1,3])` and `r as.numeric(summary_sex_frl[1,4])`, respectively. The mean math score and standard deviation for boys under the yes frl condition was `r as.numeric(summary_sex_frl[2,3])` and `r as.numeric(summary_sex_frl[2,4])`, respectively. The mean math score and standard deviation for girls under the no frl condition was `r as.numeric(summary_sex_frl[3,3])` and `r as.numeric(summary_sex_frl[3,4])`, respectively. Finally, the mean math score and standard deviation for girls under the yes frl condition was `r as.numeric(summary_sex_frl[4,3])` and `r as.numeric(summary_sex_frl[4,4])`, respectively.   


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup


\newpage

# Commit 5
```{r}

library(plyr)

data$frl <- revalue(data$frl, c("yes" = "Free/Reduced Price Meals", "no" = "Paid"))


graph <- ggplot(data, aes(x = totexp, y = tmathss)) +
  geom_point(color = "grey") +
  geom_smooth(method = lm, aes(color = frl)) +
  theme_minimal() +
  labs(title = "Relation between teacher experience and math scores", 
       subtitle = "Separate regression lines displayed by free/reduced price lunch status",
       x = "Teacher Experience (years)",
       y = "Total Math Scale Score") +
        theme(legend.position="bottom") 



graph2 <- graph + labs(color = "Lunch Status")

graph2
                       
```
\newpage
The graph demonstrates that students who pay for their lunch have higher total math scale scores than students who receive free or reduced lunch. We can also see a slight increase in students' math scores if they havea teacher with more years of teaching experience. 

